### 2014-10-02 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix typo in frontmatter
San Francisco: Add condensed figure captions

\headerC{
\flushright{
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Daniel Madrzykowski \\
{\em Fire Research Division \\
Engineering Laboratory \\

@@

\begin{tabbing}
\hspace{1.5in} \= \\
ft \> foot \\
m \> meter \\
min \> minute \\
Pa \> Pascal \\
psi \> pound per square inch \\
s \> second \\
W \> Watt \\
$k$ \> thermal conductivity \\
$\rho$ \> density \\
$c_{p}$ \> specific heat \\
\end{tabbing}

@@

\begin{table}[!ht]
\caption[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer2}}
\begin{tabular}{cl}
\toprule
Incident Time  &  Fire Behavior / Fireground Operation                                                \\
{(hh:mm:ss)}   &                                                                                      \\
\midrule
10:45:00       &  Dispatch for a curtain fire due to an electrical short at a residential structure.  \\
               &                                                                                      \\
10:48:00       &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
               &  the front door with a 1~\sfrac{3}{4}~in hoseline.                                   \\
               &                                                                                      \\
10:54:00       &  E26 crew states that the fire is located below the first floor.                     \\
               &                                                                                      \\
10:56:00       &  BC9 observes smoke but no fire at the left rear corner of the structure.            \\
               &                                                                                      \\
10:58:42       &  Fire self-vents from the rear side of the structure when a glass window in the      \\
               &  basement fails. Additional glass windows on the rear side of the structure fail     \\
               &  within the next two minutes.                                                        \\
               &                                                                                      \\
10:59:23       &  BC9 forces open the basement door on the left side of the structure,                \\
               &  reports heavy fire and smoke, and requests a second hoseline.                       \\
               &                                                                                      \\
11:00:00       &  BC6 notices a severe change in conditions (heavy black smoke from garage).          \\
               &                                                                                      \\
11:01:00       &  Heavy fire and black smoke observed at rear of structure. Incident command          \\
               &  (IC) attempts to contact E26 several times via radio with no reply.                 \\
               &                                                                                      \\
11:02:00       &  E32 crew makes entry into the basement with a second hoseline and begins            \\
               &  suppression operations.                                                             \\
               &                                                                                      \\
11:08:00       &  Two downed E26 firefighters are found on the first floor.                           \\
               &                                                                                      \\
11:09:00       &  The downed E26 firefighters are carried out of the structure.                       \\
               &                                                                                      \\
\bottomrule
\end{tabular}
\label{tab:incident_timeline}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor}
\includegraphics[width=5.0in]{../Figures/Plan_First_Floor}
\includegraphics[width=5.0in]{../Figures/Plan_Basement_Floor}
\caption[Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.]{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure. The fire originated in the living room on the basement floor. Stairs and rooms are identified using information collected by NIST.}
\label{fig:floor_plan}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5.50in]{../Figures/Post_Exterior_Front} \\
\vspace{0.1in}
\includegraphics[width=3.50in]{../Figures/Post_Exterior_Rear}
\caption{Front (top) and rear (bottom) exterior of the structure after the incident.}
\label{fig:post_exterior}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/Fire_HRR}
\caption[Prescribed HRR vs. time.]
{Prescribed HRR vs. time. The text labels indicate the three stages of the fire based on the contribution of the fuel packages.}
\label{fig:hrr}
\end{figure}

@@

\begin{table}[!ht]
\caption[Timeline of ventilation events in the simulation]{Timeline of ventilation events in the simulation}
\begin{tabular}{ccll}
\toprule
Simulation Time      &  Ventilation Area  &  Ventilation Type    &  Ventilation Location     \\
{(s)}                &  (m$^2$)           &                      &                           \\
\midrule
0                    &  1.47              &  Door                &  Front Entry Exterior     \\
0                    &  10.1              &  Overhead Door       &  Front Garage Exterior    \\
0                    &  1.68              &  Door                &  Stairwell Interior       \\
0                    &  1.68              &  Door                &  Garage Interior          \\
342                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.68              &  Door                &  Left Basement Exterior   \\
418                  &  2.52              &  Window              &  Rear Basement Exterior   \\
440                  &  2.31              &  Window              &  Rear Basement Exterior   \\
450                  &  3.78              &  Sliding Glass Door  &  Rear Basement Exterior   \\
\bottomrule
\end{tabular}
\label{tab:ventilation_timeline}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
\caption{Front (top) and rear (bottom) of the structure with a 10~cm computational mesh.}
\label{fig:SMV_exterior_grid}
\end{figure}

@@

\begin{table}[!ht]
\caption[Relevant fire model input parameters]{Relevant fire model input parameters}
\begin{tabular}{lll}
\toprule
Parameter                                    &  Description                                  &  Discussion                        \\
\midrule
Simulation Time                              &  9~min                                        &  --                                \\
Grid Cell Size                               &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
Ambient Temperature$^*$                      &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
Reaction: Polyurethane~\cite{SFPE:Tewarson}  &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.010~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 26,200~kJ/kg             &                                    \\
Reaction: Wood~\cite{SFPE:Tewarson}          &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 16,400~kJ/kg             &                                    \\
Peak HRRs                                    &  Initial couch fire: 5~MW                     &  Section~\ref{sec:fires}           \\
                                             &  Basement flashover fire: 14~MW               &                                    \\
                                             &  Basement balcony fire: 1~MW                  &                                    \\
Material: Gypsum Board~\cite{WAKILI2007}     &  Thermal conductivity: 0.28~\si{W/(m.K)}      &  Section~\ref{sec:materials}       \\
                                             &  Density: 810~kg/m$^3$                        &                                    \\
                                             &  Specific heat: 1.0~\si{kJ/(kg.K)}            &                                    \\
                                             &  Thickness: 1.2~\si{cm}                       &                                    \\
\bottomrule
\end{tabular}
\footnotesize
\\ $^{*}$Initial interior temperature was assumed to be 20~$^{\circ}$C; actual exterior temperature was 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
\normalsize
\label{tab:model_parameters}
\end{table}

@@

\caption[Fire incident and simulation event timeline]{Fire incident and simulation event timeline}

@@

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/Fire_HRR_w_FDS}
\caption[HRR vs. time from the FDS simulations.]
{HRR vs. time from the FDS simulations. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
\label{fig:hrr_w_fds}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[height=8.0in]{../Figures/Timeline_Comparison}
\caption{Comparison of on-scene photographs and Smokeview snapshots of exterior combustion occurring on the rear side of the structure. The on-scene time is indicated on the left photograph, and the corresponding simulation time is indicated on the right Smokeview snapshot. For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
\label{fig:timeline_comparison_rear}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Photo_Front_350_s}
\includegraphics[width=5.0in]{../Figures/SMV_Front_350_s}
\caption{Comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure. The on-scene time is indicated on the photograph (top), and the corresponding simulation time is indicated on the Smokeview snapshot (bottom). For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
\label{fig:timeline_comparison_front}
\end{figure}

@@

In this figure, the pressure profile within the high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions. The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed. After the rear basement windows failed, the pressure rise in the basement ranged from a 5~Pa ($7.3 \times 10^{-4}$~psi) over-pressure at mid-level height to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/SMV_Pres_340_s}
\input{../Figures/colorbar_metric_pres}
\includegraphics[width=5.5in]{../Figures/SMV_Pres_343_s}
\input{../Figures/colorbar_metric_pres}
\caption{FDS simulated pressure contours, 2~s before (top) and 1~s after (bottom) first rear basement window failure (342~s). The fire originated in the living room in the basement.}
\label{fig:smv_pressure}
\end{figure}

@@

In this figure, the velocity profile within the high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions. The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption{FDS simulated velocity contours, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption{FDS simulated velocity vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity_vectors}
\end{figure}

@@

Analysis of the temperatures from the simulation focuses on the high hazard areas of the structure: the basement and the interior stairwell which connects the basement to the exhaust vents/doors on the front side of the structure (the front door and the garage door). The temperature contours shown in Fig.~\ref{fig:smv_temperature} indicate the gas temperatures within the structure before and after the rear basement window failures.

In this figure, The temperature profile at these high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions. The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{FDS simulated temperature contours, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{FDS simulated temperature vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_First_Floor}
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_Basement_Floor}
\caption{Summary of simulated flow path in the stairwell on the first floor and basement floor 120~s after the first rear basement window failure. The arrows indicate the direction of flow. Two arrows located at a door or window indicate bi-directional flow at a vent opening. The maximum velocity is indicated by the red contour and corresponds to 9~m/s (20~mph).}
\label{fig:flow_path_top}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure (342~s).}
\label{fig:smv_flow_path_top_1}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_462_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure (342~s).}
\label{fig:smv_flow_path_top_2}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Drawing_Second_Floor_Metric}
\caption[Dimensioned drawing of the second floor.]{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_second_floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Drawing_First_Floor_Metric}
\caption[Dimensioned drawing of the first floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_first_floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Drawing_Basement_Metric}
\caption[Dimensioned drawing of the basement.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_basement}
\end{figure}

>>>>

\headerC{
\flushright{
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Daniel Madrzykowski \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\begin{tabbing}
\hspace{1.5in} \= \\
ft \> foot \\
m \> meter \\
min \> minute \\
Pa \> Pascal \\
psi \> pound per square inch \\
s \> second \\
W \> Watt \\
\end{tabbing}

@@

\begin{table}[!ht]
\caption[Abridged NIOSH approximate fire event timeline]
{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer2}}
\begin{tabular}{cl}
\toprule
Incident Time  &  Fire Behavior / Fireground Operation                                                \\
{(hh:mm:ss)}   &                                                                                      \\
\midrule
10:45:00       &  Dispatch for a curtain fire due to an electrical short at a residential structure.  \\
               &                                                                                      \\
10:48:00       &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
               &  the front door with a 1~\sfrac{3}{4}~in hoseline.                                   \\
               &                                                                                      \\
10:54:00       &  E26 crew states that the fire is located below the first floor.                     \\
               &                                                                                      \\
10:56:00       &  BC9 observes smoke but no fire at the left rear corner of the structure.            \\
               &                                                                                      \\
10:58:42       &  Fire self-vents from the rear side of the structure when a glass window in the      \\
               &  basement fails. Additional glass windows on the rear side of the structure fail     \\
               &  within the next two minutes.                                                        \\
               &                                                                                      \\
10:59:23       &  BC9 forces open the basement door on the left side of the structure,                \\
               &  reports heavy fire and smoke, and requests a second hoseline.                       \\
               &                                                                                      \\
11:00:00       &  BC6 notices a severe change in conditions (heavy black smoke from garage).          \\
               &                                                                                      \\
11:01:00       &  Heavy fire and black smoke observed at rear of structure. Incident command          \\
               &  (IC) attempts to contact E26 several times via radio with no reply.                 \\
               &                                                                                      \\
11:02:00       &  E32 crew makes entry into the basement with a second hoseline and begins            \\
               &  suppression operations.                                                             \\
               &                                                                                      \\
11:08:00       &  Two downed E26 firefighters are found on the first floor.                           \\
               &                                                                                      \\
11:09:00       &  The downed E26 firefighters are carried out of the structure.                       \\
               &                                                                                      \\
\bottomrule
\end{tabular}
\label{tab:incident_timeline}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor}
\includegraphics[width=5.0in]{../Figures/Plan_First_Floor}
\includegraphics[width=5.0in]{../Figures/Plan_Basement_Floor}
\caption[Plan view of second floor, first floor, and basement floor of structure.]
{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure. The fire originated in the living room on the basement floor. Stairs and rooms are identified using information collected by NIST.}
\label{fig:floor_plan}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5.50in]{../Figures/Post_Exterior_Front} \\
\vspace{0.1in}
\includegraphics[width=3.50in]{../Figures/Post_Exterior_Rear}
\caption[Front and rear exterior of the structure after the incident.]
{Front (top) and rear (bottom) exterior of the structure after the incident.}
\label{fig:post_exterior}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/Fire_HRR}
\caption[Prescribed HRR vs. time for the simulation.]
{Prescribed HRR vs. time for the simulation. The text labels indicate the three stages of the fire based on the contribution of the fuel packages.}
\label{fig:hrr}
\end{figure}

@@

\begin{table}[!ht]
\caption[Timeline of ventilation events in the simulation]
{Timeline of ventilation events in the simulation}
\begin{tabular}{ccll}
\toprule
Simulation Time      &  Ventilation Area  &  Ventilation Type    &  Ventilation Location     \\
{(s)}                &  (m$^2$)           &                      &                           \\
\midrule
0                    &  1.47              &  Door                &  Front Entry Exterior     \\
0                    &  10.1              &  Overhead Door       &  Front Garage Exterior    \\
0                    &  1.68              &  Door                &  Stairwell Interior       \\
0                    &  1.68              &  Door                &  Garage Interior          \\
342                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
383                  &  1.68              &  Door                &  Left Basement Exterior   \\
418                  &  2.52              &  Window              &  Rear Basement Exterior   \\
440                  &  2.31              &  Window              &  Rear Basement Exterior   \\
450                  &  3.78              &  Sliding Glass Door  &  Rear Basement Exterior   \\
\bottomrule
\end{tabular}
\label{tab:ventilation_timeline}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
\caption[Front and rear of the structure with a 10~cm computational mesh.]
{Front (top) and rear (bottom) of the structure with a 10~cm computational mesh.}
\label{fig:SMV_exterior_grid}
\end{figure}

@@

\begin{table}[!ht]
\caption[Relevant fire model input parameters]
{Relevant fire model input parameters}
\begin{tabular}{lll}
\toprule
Parameter                                    &  Description                                  &  Discussion                        \\
\midrule
Simulation Time                              &  9~min                                        &  --                                \\
Grid Cell Size                               &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
Ambient Temperature$^*$                      &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
Reaction: Polyurethane~\cite{SFPE:Tewarson}  &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.010~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 26,200~kJ/kg             &                                    \\
Reaction: Wood~\cite{SFPE:Tewarson}          &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     &  Section~\ref{sec:fires}           \\
                                             &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
                                             &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                             &  Heat of combustion: 16,400~kJ/kg             &                                    \\
Peak HRRs                                    &  Initial couch fire: 5~MW                     &  Section~\ref{sec:fires}           \\
                                             &  Basement flashover fire: 14~MW               &                                    \\
                                             &  Basement balcony fire: 1~MW                  &                                    \\
Material: Gypsum Board~\cite{WAKILI2007}     &  Thermal conductivity: 0.28~\si{W/(m.K)}      &  Section~\ref{sec:materials}       \\
                                             &  Density: 810~kg/m$^3$                        &                                    \\
                                             &  Specific heat: 1.0~\si{kJ/(kg.K)}            &                                    \\
                                             &  Thickness: 1.2~\si{cm}                       &                                    \\
\bottomrule
\end{tabular}
\footnotesize
\\ $^{*}$Initial interior temperature was assumed to be 20~$^{\circ}$C; actual exterior temperature was 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
\normalsize
\label{tab:model_parameters}
\end{table}

@@

\caption[Fire incident and simulation event timeline]
{Fire incident and simulation event timeline}

@@

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/Fire_HRR_w_FDS}
\caption[Predicted HRR vs. time from the FDS simulation.]
{Predicted HRR vs. time from the FDS simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
\label{fig:hrr_w_fds}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[height=8.0in]{../Figures/Timeline_Comparison}
\caption[Snapshots of exterior combustion occurring on the rear side of the structure.]
{Comparison of on-scene photographs and Smokeview snapshots of exterior combustion occurring on the rear side of the structure. The on-scene time is indicated on the left photograph, and the corresponding simulation time is indicated on the right Smokeview snapshot. For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
\label{fig:timeline_comparison_rear}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Photo_Front_350_s}
\includegraphics[width=5.0in]{../Figures/SMV_Front_350_s}
\caption[Snapshot of smoke coming out of the front side of the structure.]
{Comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure. The on-scene time is indicated on the photograph (top), and the corresponding simulation time is indicated on the Smokeview snapshot (bottom). For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
\label{fig:timeline_comparison_front}
\end{figure}

@@

In this figure, the pressure profile within the high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions. The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed. After the rear basement windows failed, the pressure rise in the basement ranged from a 5~Pa ($7.3 \times 10^{-4}$~psi) over-pressure at mid-level height to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.

\begin{figure}[!ht]
\includegraphics[width=5.5in]{../Figures/SMV_Pres_340_s}
\input{../Figures/colorbar_metric_pres}
\includegraphics[width=5.5in]{../Figures/SMV_Pres_343_s}
\input{../Figures/colorbar_metric_pres}
\caption[Simulated pressure contours on the right interior side of the structure.]
{Simulated pressure contours on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) first rear basement window failure (342~s). The fire originated in the living room in the basement.}
\label{fig:smv_pressure}
\end{figure}

@@

In this figure, the velocity profile within the high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions. The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity contours on the right interior side of the structure.]
{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
\input{../Figures/colorbar_metric_velo}
\input{../Figures/colorbar_std_velo}
\caption[Simulated velocity vectors on the right interior side of the structure.]
{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_velocity_vectors}
\end{figure}

@@

Analysis of the temperatures from the simulation focuses on the high-hazard areas of the structure: the basement and the interior stairwell which connects the basement to the exhaust vents/doors on the front side of the structure (the front door and the garage door). The temperature contours shown in Fig.~\ref{fig:smv_temperature} indicate the gas temperatures within the structure before and after the rear basement window failures.

In this figure, The temperature profile at these high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions. The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the right interior side of the structure.]
{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature vectors on the right interior side of the structure.]
{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
\label{fig:smv_temperature_vectors}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_First_Floor}
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_Basement_Floor}
\caption[Top view of the simulated flow path in the interior stairwell.]
{Top view of the simulated flow path on the first floor and basement floor 120~s after the first rear basement window failure. The arrows indicate the direction of flow. Two arrows located at a door or window indicate bi-directional flow at a vent opening. The maximum velocity is indicated by the red contour and corresponds to 9~m/s (20~mph).}
\label{fig:flow_path_top}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor before basement window failure.]
{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure (342~s).}
\label{fig:smv_flow_path_top_1}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_402_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_462_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours on the first floor after basement window failure.]
{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure (342~s).}
\label{fig:smv_flow_path_top_2}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Drawing_Second_Floor_Metric}
\caption[Dimensioned drawing of the second floor.]
{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_second_floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Drawing_First_Floor_Metric}
\caption[Dimensioned drawing of the first floor.]
{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_first_floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Drawing_Basement_Metric}
\caption[Dimensioned drawing of the basement floor.]
{Dimensioned drawing of the basement floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_basement}
\end{figure}
